Maximum Entropy Spectral Analysis: a case study

### 2021-03-05 paper/mesa.tex
added opt plots
Removed old img + some changes

>>>>

\subsection{How well the autoregressive order is recovered?}

\begin{figure}
	\centering
	\includegraphics[width = \linewidth]{Images/arp_errors/scatter_deltap_ptrue}
	\caption{Reconstructed value for the autoregressive order plotted against the true value of the autoregressive order.
	The reconstructed autoregressive orders are computed from a time series randomly drawn with an $AR(p)$ model, with the three different loss functions under investigation.
	}
	\label{fig:p_vs_ptrue}
\end{figure}

We now address the issue of how well the autoregressive order (i.e. the number of $a_k$ coefficients employed) is estimated with each loss function.
In doing so, we generate $100$ autoregressive processes $AR(p)$ with a random value of $p$, drawn such that $log(p)~\mathcal{U}[log(2), log(5000)]$.
Each coefficient $a_k$ is assigned as follows: $a_k = \alpha_k e^{-0.05\cdot k}$, where $\alpha ~ \mathbb{N}(0,0.1)$ and the exponential ensures that the coefficients falls with distance (as in any realistic finite memory process).
We report the result of this investigation in fig.~\ref{fig:p_vs_ptrue}

Observations below!!!!
